Distinction Centrality Analysis

### 2025-07-17 analysis.qmd
do it# Please enter the commit message for your changes. Lines starting

```{r}
   make.broker.graphs <- function(n = 10) {
      g <- make_empty_graph(9, directed = FALSE)
      g <- g + edge(1,2)
      g <- g + edge(1,3)
      g <- g + edge(2,4)
      g <- g + edge(2,5)
      g <- g + edge(2,6)
      g <- g + edge(3,7)
      g <- g + edge(3,8)
      g <- g + edge(3,9)
      el <- vector(mode = "list", length = n)
      el[[1]] <- g
      a <- 10
      b <- 11
      c <- 12
      d <- 13
      for (i in 2:n) {
         g <- add_vertices(g, 4)
         g <- g + edge(1,a)
         g <- g + edge(a,b)
         g <- g + edge(a,c)
         g <- g + edge(a,d)
         el[[i]] <- g
         a <- a + 4
         b <- b + 4
         c <- c + 4
         d <- d + 4
      }
   return(el)
   }
   b <- make.broker.graphs(30)
   c <- lapply(b, distinction)
   d <- sapply(c, function(x) {x[2, 2]})
```

@@

```{r}
   dat <- data.frame(d = d, n = 1:length(d))
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p

>>>>

```{r}
   make.broker.graphs <- function(n = 10) {
      g <- make_empty_graph(9, directed = FALSE)
      g <- g + edge(1,2)
      g <- g + edge(1,3)
      g <- g + edge(2,4)
      g <- g + edge(2,5)
      g <- g + edge(2,6)
      g <- g + edge(3,7)
      g <- g + edge(3,8)
      g <- g + edge(3,9)
      el <- vector(mode = "list", length = n)
      el[[1]] <- g
      a <- 10
      b <- 11
      c <- 12
      d <- 13
      for (i in 2:n) {
         g <- add_vertices(g, 4)
         g <- g + edge(1,a)
         g <- g + edge(a,b)
         g <- g + edge(a,c)
         g <- g + edge(a,d)
         el[[i]] <- g
         a <- a + 4
         b <- b + 4
         c <- c + 4
         d <- d + 4
      }
   return(el)
   }
   b <- make.broker.graphs(30)
   c <- lapply(b, distinction)
   e <- sapply(c, function(x) {x[nrow(x), 2]})

@@

```{r}
   d <- sapply(c, function(x) {x[1, 3]})
   dat <- data.frame(d = d, n = 1:length(d)) |> 
      mutate(n = n + 1)
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   #p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p <- p + ggtitle("Scalar Distinction of Star Node")
   p
   ggsave(here("Plots", "star-by-nbranches.png"), width = 7, height = 7, units = "in")
```

```{r}
   d <- sapply(c, function(x) {x[2, 3]})
   dat <- data.frame(d = d, n = 1:length(d)) |> 
      mutate(n = n + 1)
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   #p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p <- p + ggtitle("Scalar Distinction of Star Node")
   p
   ggsave(here("Plots", "gatekeeper-by-nbranches.png"), width = 7, height = 7, units = "in")
```

```{r}
   d <- sapply(c, function(x) {x[nrow(x), 3]})
   dat <- data.frame(d = d, n = 1:length(d)) |> 
      mutate(n = n + 1)
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p
   ggsave(here("Plots", "pendant-by-nbranches.png"), width = 7, height = 7, units = "in")
```
